---
title: "Untitled"
author: "Michael E. Colvin"
date: "Monday, June 06, 2016"
output: html_document
---

Objective:  Evaluate whether sapply, vapply, or which is the best approach for simulating pallid sturgeon dynamics on an individual level.

First the packages we will need for benchmarking.

```{r}
library(microbenchmark)
library(ggplot2)
```

Now we can set up some biggish matrices to apply functions to, like we would in the Pallid Sturgeon model.


```{r}
daug<- 50000
nreps<- 10
Z<-W<- matrix(0,daug,nreps)
```

Now we can population the matrices

```{r}
for(i in 1:nreps)
    {
    Z[,i]<- rbinom(daug,1,0.8) 
    W[,i]<- runif(daug,100,1500)
    }
W<- W*Z

indx<- lapply(1:nreps,function(x) which(Z[,x]==1))
tmp<- unlist(lapply(1:nreps,function(x) length(indx[[x]])))
indx<- cbind(unlist(indx),sort(rep(1:nreps,tmp)))
```



```{r}

mbm=microbenchmark(
one=sapply(1:nreps,function(x)
    {
    rlnorm(nrow(W),W[,x]*Z[,x],0.1)
    }),
two= rlnorm(nrow(indx),W[indx],0.1),
times=500)

autoplot(mbm)


one<-c()
for(i in 1:100)
  {
  ptm<-proc.time()
W[]<-sapply(1:nreps,function(x)
    {
    rlnorm(nrow(W),W[,x]*Z[,x],0.1)
    })
   tm<- (proc.time()-ptm)[3]
  one<-c(one,tm) 
  }


two<-c()
for(i in 1:100)
  {
  ptm<-proc.time()
  indx<- lapply(1:nreps,function(x) which(Z[,x]==1))
  tmp<- unlist(lapply(1:nreps,function(x) length(indx[[x]])))
  indx<- cbind(unlist(indx),sort(rep(1:nreps,tmp)))
  W[indx]<-rlnorm(nrow(indx),W[indx],0.1)
  tm<- (proc.time()-ptm)[3]
  two<-c(two,tm)
  }



boxplot(cbind(one,two))

```






You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
