---
title: "Evaluating using spatial rather than temporal replicates in N mixture models"
author: "Michael E. Colvin"
date: "Friday, October 16, 2015"
output: html_document
---


```{r}
library(unmarked)
?pcount

```

First let simulate some data that is similar to what you collected over the 4 years of the study.  I took some liberties in associations of data.


```{r}
# Simulate data
set.seed(1234)# SO YOU CAN REPLICATE THIS

Nwetlands<- 35
Nvisits<- 17 # number of visits to each wetland each year
Nyears<- 4 # number years of the study

# DETECTION COVARIATES
observers<- c('mk',"thing1","thing2")

# ABUNDANCE COVARIATES
## TIME VARYING
salinity<- runif(Nvisits*Nyears*Nwetlands, 0,100000)# salnity in ppm
salinity<- matrix(salinity, Nwetlands*Nyears, Nvisits)
## WETLAND LEVEL
area<- runif(Nwetlands, 10,300)
area<- area[sort(rep(c(1:Nwetlands),Nyears))]
```

## Abundance

```{r}
B0_salinity<- 0.01
B1_salinity<- 0.002
lambda <- exp(beta0 + beta1*x)   # expected counts at each site
N <- rpois(nSites, lambda)       # latent abundance


```

## Detection
Next step is to set up the detection probabilities.  Here I am going to make a matrix of detecton pr

```{r}
y <- matrix(NA, Nwetlands*Nyears, Nvisits)
# detection prob for each visit, assumes p is constant among sites during visits

p <- c(0.3, 0.6, 0.8) 
for(i in 1:Nwetlands*Nyears)
    {
  for(j in 1:nVisits) 
      {
      y[,j] <- rbinom(nSites, N, p[i,j])
      }
  }
```

```{r}
# Organize data
visitMat <- matrix(as.character(1:nVisits), nSites, nVisits, byrow=TRUE)

umf <- unmarkedFramePCount(y=y, siteCovs=data.frame(x=x),
    obsCovs=list(visit=visitMat))
summary(umf)
```

```{r}
# Fit a model
fm1 <- pcount(~visit-1 ~ x, umf, K=50)
fm1

plogis(coef(fm1, type="det")) # Should be close to p

```





nSites <- 100
nVisits <- 3
x <- rnorm(nSites)               # a covariate
beta0 <- 0
beta1 <- 1
lambda <- exp(beta0 + beta1*x)   # expected counts at each site
N <- rpois(nSites, lambda)       # latent abundance
y <- matrix(NA, nSites, nVisits)
p <- c(0.3, 0.6, 0.8)            # detection prob for each visit
for(j in 1:nVisits) {
  y[,j] <- rbinom(nSites, N, p[j])
  }

# Organize data
visitMat <- matrix(as.character(1:nVisits), nSites, nVisits, byrow=TRUE)

umf <- unmarkedFramePCount(y=y, siteCovs=data.frame(x=x),
    obsCovs=list(visit=visitMat))
summary(umf)

# Fit a model
fm1 <- pcount(~visit-1 ~ x, umf, K=50)
fm1

plogis(coef(fm1, type="det")) # Should be close to p


# Empirical Bayes estimation of random effects
(fm1re <- ranef(fm1))
plot(fm1re, subset=site %in% 1:25, xlim=c(-1,40))
sum(bup(fm1re))         # Estimated population size
sum(N)                  # Actual population size



````